---
title: "Demonstration"
author: "Jianing Yao"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Demonstration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


This vignette demonstrates the usage of `MCMCpack` on a `TidyTuesday` dataset. 

**Data**: The Broadway Weekly Grosses data can be obtained from [TidyTuesday](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-04-28/readme.md). 

**Question**: This data contains information about weekly box office grosses, attendance, ticket prices of shows presented in Broadway theatres. What factors will impact weekly box office revenues, e.g., ticket price, attendance, time of the year?

**Data dictionary**: The data dictionary can be obtained [here](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-04-28/readme.md).


```{r}
## create `data` directory if it doesn't exist
if (!dir.exists("../data")) {
  dir.create("../data")
}
## download the TidyTuesday dataset only if it doesn't exist
if (!file.exists("../data/grosses.rda")) {
  grosses <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-04-28/grosses.csv', guess_max = 40000)
  usethis::use_data(grosses)
}
if (!file.exists("../data/synopses.rda")) {
  synopses <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-04-28/synopses.csv')
  usethis::use_data(synopses)
}
if (!file.exists("../data/cpi.rda")) {
  cpi <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-04-28/cpi.csv')
  usethis::use_data(cpi)
}
```

```{r}
## load data set
load("../data/grosses.rda")
load("../data/synopses.rda")
load("../data/cpi.rda")
```


### Data wrangling and visualization

**First, I selected data after year 2010 and created a dummy variable to indicate whether the record is in holiday months (December or January).**

```{r}
library(dplyr)
library(lubridate)
library(purrr)
library(ggplot2)

df <- grosses %>%
  mutate(year = year(week_ending),
         month = month(week_ending),
         is_dec_or_jan = ifelse(month %in% c(12, 1), 1, 0)) %>%
  select(-week_number, -performances, -previews, -seats_sold, -seats_in_theatre, 
         -potential_gross, -top_ticket_price, -show) %>%
  filter(year >= 2010, complete.cases(.)) %>%
  mutate(theatre = as.factor(theatre))

```

**The plot below shows the trend of weekly gross from 2010 to 2020.**

```{r fig.width=7, fig.height=5}
ggplot(df, aes(x = week_ending, y = weekly_gross_overall/100000)) +
  geom_line() + 
  labs(title = "Weekly Gross Over Time (per $100, 000)",
       x = "Week Ending",
       y = "Weekly Gross Overall (per $100, 000)",
       caption = "Data Source: Broadway Grosses") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  theme_minimal()
```

**The figure below shows the mean of weekly box office gross, average ticket price, and percent of theatre capacity for individual shows from 2010 to 2020.**

```{r fig.width=7, fig.height=5}
library(tidyr)
df_theatre <- df %>%
  select(theatre, weekly_gross, avg_ticket_price, pct_capacity) %>%
  split(.$theatre)
means <- map_dfr(df_theatre, ~ colMeans(select(.x, -1), na.rm = TRUE), .id = "theatre") %>%
  arrange(desc(weekly_gross))

means_long <- means %>%
  pivot_longer(-theatre, names_to = "Metric", values_to = "value") %>%
  mutate(Metric = recode(Metric,
                         weekly_gross = "Weekly Gross",
                         avg_ticket_price = "Average Ticket Price",
                         pct_capacity = "Percent Capacity"))

ggplot(means_long, aes(x = theatre, y = value, fill = Metric)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  facet_wrap(~ Metric, scales = "free_y", nrow = 3) +
  labs(title = "Mean Theatre Metrics", x = "Theatres", y = "Value") +
  theme(
    axis.text.x = element_blank(),  
    axis.ticks.x = element_blank(),  
    legend.position = "bottom"
  ) 

```

### Try out `MCMCpack`

**Next, I tried out Bayesian linear regression using Markov Chain Monte Carlo sampling algorithm with three predictors: average ticket price, percent of theatre capacity, and whether happens in holiday months. Weak priors are used for beta and sigma^2. Sub-models are also fitted and compared with the full model based on Bayes factor to select the best model.** 

```{r setup}
library(MCMCpack)

numeric_predictors <- c("avg_ticket_price", "pct_capacity")
df_bayes <- df %>%
  modify_at(vars(one_of(numeric_predictors)), ~ as.vector(scale(.)))
  

## MCMCpack
# Define predictor combinations
predictor_combinations <- list(
  c("avg_ticket_price"),
  c("pct_capacity"),
  c("is_dec_or_jan"),
  c("avg_ticket_price", "pct_capacity"),
  c("avg_ticket_price", "is_dec_or_jan"),
  c("pct_capacity", "is_dec_or_jan"),
  c("avg_ticket_price", "pct_capacity", "is_dec_or_jan")
)

model_summaries <- list()
models <- list()

# Fit models and store summaries in the list
for (combo in predictor_combinations) {
  formula <- as.formula(paste("weekly_gross ~", paste(combo, collapse = " + ")))
  model <- MCMCregress(formula, data = df_bayes, B0 = 10e-8,
                       mcmc = 10000, marginal.likelihood="Chib95")
  summary <- summary(model)
  models[[paste(combo, collapse = "_")]] <- model
  model_summaries[[paste(combo, collapse = "_")]] <- summary
}

sub1 <- models$avg_ticket_price
sub2 <- models$pct_capacity
sub3 <- models$is_dec_or_jan
sub4 <- models$avg_ticket_price_pct_capacity
sub5 <- models$avg_ticket_price_is_dec_or_jan
sub6 <- models$pct_capacity_is_dec_or_jan
full <- models$avg_ticket_price_pct_capacity_is_dec_or_jan

BF <- BayesFactor(sub1, sub2, sub3, sub4, sub5, sub6, full)
PostProbMod(BF)

```

**Not surprisingly, the best model is the full model that has the highest posterior probability of the model. All three predictors are significant based on posterior distributions.**

```{r}
full <- MCMCregress(weekly_gross ~ avg_ticket_price + pct_capacity + is_dec_or_jan, data = df_bayes)
summary(full)
```

**Finally, I plotted the fitted values using Bayesian estimated coefficients against the true values of weekly gross to evaluate performance.**

```{r fig.width=7, fig.height=5}
estimates <- map(as.data.frame(full), mean)
df_bayes$fitted <- estimates$`(Intercept)` + 
                   estimates$avg_ticket_price * df_bayes$avg_ticket_price +
                   estimates$pct_capacity * df_bayes$pct_capacity +
                   estimates$is_dec_or_jan * df_bayes$is_dec_or_jan
ggplot(data = df_bayes, aes(x = weekly_gross, y = fitted)) +
  geom_point() +
  geom_abline(slope = 1, intercept = 0, color = "blue", linetype = "dashed") +
  labs(title = "True value of weekly gross against fitted using Bayesian estimated coefficients", 
       x = "True value", 
       y = "Fitted value") +
  theme_minimal()

```


### Summary
From this simple analysis, average ticket price, percentage of theatre capacity (i.e., attendence), and whether the shows are on during the holiday months can predict weekly box office gross of Broadway shows. The Bayesian approach provides another point of view to validate my assumption.

### Functions
- Data wrangling: 
  - `dplyr`: `mutate()`, `select()`, `filter()`, `arrange()`, `recode()`
  - `tidyr`: `pivot_longer()`
  - `lubridate`: `year()`, `month()`
- purr: `map_dfr()`, `modify_at()`, `map()`
- Plot: `geom_line()`, `geom_bar()`, `geom_point()`, `geom_abline()`, `facet_wrap()`
- Package: `MCMCregress()`, `BayesFactor()`, `PostProbMod()`


